Select-based random access to variable-byte encodings

### 2020-03-05 gradu/msc_english_contents.tex
Changes

@@

 - 4bit is naturally slower, because of smaller block size
 - select is better with longer numbers, because it only needs 1 select call and reads straight from memory

>>>>

 - TODO figure out why 4bit crashes sometimes with 500M_all

@@

 - 4bit is naturally slower, because of smaller block size

 - actually may not be the case with select (maybe cache is causing this?)

 - better dataset might be something with larger (like 60bit) numbers

 - select is better with longer numbers, because it only needs 1 select call and reads straight from memory
